\documentclass[letterpaper]{article}

\usepackage{preamble}
\addbibresource{refs.bib}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
 
\title{Modelling Surface Acoustic Wave Driven Thin Film Flows over Topography}
\author{Bhargav Samineni}
\date{\today}

\begin{document}
 
\maketitle 

\begin{abstract}
    Motivated by the acoustowetting phenomenon and its applications to the dynamic wetting 
    of objects by a coating liquid, we explore the influence of surface acoustic waves and gravity on the motion of a thin film
    flowing over a surface. We consider surfaces that may be both inclined and include topographical features like trenches, mounds, bumps, etc. 
    Using the lubrication approximation, we reduce the equations of motion for the film
    to a single nonlinear partial differential equation that describes the evolution of the film height relative to the 
    surface topography in time and space. 
\end{abstract}
  
%\dosecttoc
%\tableofcontents
 
\section{Introduction}
The motion of thin liquid films with fronts is a relatively
ubiquitous dynamic in nature that also has applications to a number of technical fields and processes. 
Particularly with respect to coating processes, the influence of other factors besides viscous and surface tension
forces (such as gravity \cite{diez2002computing} and electric fields \cite{veremieiev2012electrified}) has also been 
studied. Recent experiments have shown that high frequency surface acoustic waves may be a novel method 
for coating techniques, particularly between two liquids where one of the liquids is not influenced by the acoustic streaming, so in this report we study the affect of these acoustic waves on the dynamics 
of thin liquid films. Specifically, we approach the problem using the lubrication approximation to reduce the 
Navier-Stokes equations into a single nonlinear PDE and simplify the interactions between the two liquids
by considering the stationary one to be a topographical feature of our surface. Both the influence of surface acoustic
waves on the spreading of liquid films (see \cite{altshuler2016free}) and coating over topography with gravity as the primary driving have been previously 
studied (see \cite{kalliadasis2000steady,stillwagon1988topo,veremieiev2011gravity}), but to the best of our knowledge the 
intersection of these two interactions has not been studied. 

\section{Governing Equation} \label{sec:gov_eq}
\input{sections/thinfilm_saw.tex}
 
\section{Method of Solution} \label{sec:method_of_sol}
\input{sections/num_sol.tex}
 
%\begin{figure}[h]  
%    \centering
%    \resizebox{.75\linewidth}{!}{\input{images/test/plt.tex}}
%    \caption{A sample image}
%\end{figure}
 
\newpage
\begin{appendices}
    \section{Topography Definitions} \label{sec:topography}

    \section{Spatial Discretization Expanded}\label{sec:space_discrete_expand}
    \input{sections/discretization.tex}
\end{appendices}

\newpage
\printbibliography

\end{document} 